\ipiitem{extras}{The additional data returned by the client code, printed verbatim. Will print
                             out one file per bead, unless the bead attribute is set by the user.}{}\ipiitem{f\_centroid}{The force acting on the centroid.}{dimension: force; }\ipiitem{forces}{The force trajectories. Will print out one file per bead, unless the bead attribute is set by the user.}{dimension: force; }\ipiitem{isotope\_zetasc}{Scaled-coordinates isotope fractionation direct estimator in the form of ratios of partition functions. Takes two arguments, 'alpha' , which gives the
                      scaled mass parameter and default to '1.0', and 'atom', which is the label or index of a type of atoms. All the atoms but the selected ones
                      will have zero output}{}\ipiitem{isotope\_zetatd}{Thermodynamic isotope fractionation direct estimator in the form of ratios of partition functions. Takes two arguments, 'alpha' , which gives the
                      scaled mass parameter and default to '1.0', and 'atom', which is the label or index of a type of atoms. All the atoms but the selected ones
                      will have zero output}{}\ipiitem{kinetic\_cv}{The centroid virial quantum kinetic energy estimator for each atom, resolved into Cartesian components $[$xx, yy, zz$]$}{dimension: energy; }\ipiitem{kinetic\_od}{The off diagonal elements of the centroid virial quantum kinetic energy tensor $[$xy, xz, yz$]$}{dimension: energy; }\ipiitem{momenta}{The momentum trajectories. Will print out one file per bead, unless the bead attribute is set by the user.}{dimension: momentum; }\ipiitem{p\_centroid}{The centroid momentum.}{dimension: momentum; }\ipiitem{positions}{The atomic coordinate trajectories. Will print out one file per bead, unless the bead attribute is set by the user.}{dimension: length; }\ipiitem{r\_gyration}{The radius of gyration of the ring polymer, for each atom and resolved into Cartesian components $[$xx, yy, zz$]$}{dimension: length; }\ipiitem{v\_centroid}{The centroid velocity.}{dimension: velocity; }\ipiitem{velocities}{The velocity trajectories. Will print out one file per bead, unless the bead attribute is set by the user.}{dimension: velocity; }\ipiitem{x\_centroid}{The centroid coordinates.}{dimension: length; }